Inferring fine scale wild species distribution from spatially aggregated data

### 2022-10-21 Version_M2_plusieurszones/draft/paper_3/paper_3.Rmd
modif

floatsintext     : yes
figurelist       : no
tablelist        : no
footnotelist     : no
linenumbers      : yes
mask             : no
draft            : no

@@

## Table of convergence
Results_conv <- Results
Results_conv$one <- 1
Results_conv_2 <- summaryBy(Convergence+one~
                              sequencesdepeche+
                              # zonespersequence+
                              aggreg_obs+
                              # b_true+
                              n_samp_com+
                              reallocation,
                            data=Results_conv,
                            FUN=sum) %>%
  dplyr::select(n_samp_com,
                sequencesdepeche,
                # zonespersequence,
                reallocation,
                aggreg_obs,
                Convergence.sum,
                one.sum) %>%
    mutate(aggreg_obs = ifelse(aggreg_obs == T,"Dj","Yi"),
           reallocation = ifelse(reallocation == 1,"Yes","No"),
           perc_convergence = round((1 - Convergence.sum / one.sum)*100,digits = 3)) %>%
  mutate(aggreg_obs = ifelse((aggreg_obs == "Yi" & reallocation == "Yes"),"Yr",aggreg_obs))

@@

Results <- Results %>%
  mutate(relloc_aggreg = paste0("Reallocation: ",ifelse(reallocation==0,"No","Yes")," -  Likelihood: ",ifelse(aggreg_obs==T,"Dj","Yi"))) %>%
  mutate(relloc_aggreg = ifelse(aggreg_obs == F & reallocation == 1,"Reallocation: Yes -  Likelihood: Yr",relloc_aggreg))

Results$zonespersequence <- as.factor(Results$zonespersequence)
Results$b_true <- as.factor(Results$b_true)
Results$relloc_aggreg <- factor(Results$relloc_aggreg,
                                levels = c("Reallocation: No -  Likelihood: Yi",
                                           "Reallocation: Yes -  Likelihood: Yr",
                                           "Reallocation: Yes -  Likelihood: Dj"))

@@

MSPE_S_plot <- ggplot()+
  geom_boxplot(data = Results_2,
               aes(x = zonespersequence,
                   y = mspe,
                   fill = relloc_aggreg),
               outlier.colour = NA)+
  theme_bw()+
  facet_wrap(.~factor(n_samp_com))+
  theme(legend.title = element_blank(),
        legend.position = "none",
        aspect.ratio = 1)+
  ylab("MSPE")+
  xlab("")+
  scale_y_log10(breaks = trans_breaks("log10", function(x) 10^x),
                labels = trans_format("log10", math_format(10^.x)))+
  scale_fill_manual(breaks = c("Reallocation: No -  Likelihood: Yi",
                                "Reallocation: Yes -  Likelihood: Yr",
                                "Reallocation: Yes -  Likelihood: Dj"),
                     values=c("gold","#F8766D","#00BA38"))

Beta_plot <- ggplot()+
  geom_boxplot(data = Results_2,
               aes(x = zonespersequence,
                   y = beta1_est,
                   fill = relloc_aggreg),
               outlier.colour = NA)+
  geom_hline(yintercept = 0,linetype="dashed")+
  geom_hline(yintercept = 2,col="red",linetype="dashed")+
  theme_bw()+
  facet_wrap(.~factor(n_samp_com))+
  theme(legend.title = element_blank(),
        legend.position = "none",
        aspect.ratio = 1)+
  # ylim(-1,1)+ 
  ylab(parse(text = TeX('$\\beta_S$')))+
  xlab("")+
  scale_fill_manual(breaks = c("Reallocation: No -  Likelihood: Yi",
                                "Reallocation: Yes -  Likelihood: Yr",
                                "Reallocation: Yes -  Likelihood: Dj"),
                     values=c("gold","#F8766D","#00BA38"))

RelBias_N_plot <- ggplot()+
  geom_boxplot(data = Results_2,
               aes(x = zonespersequence,
                   y = RelBias_N,
                   fill = relloc_aggreg),
               outlier.colour = NA)+
  geom_hline(yintercept = 0,linetype="dashed")+
  theme_bw()+
  facet_wrap(.~factor(n_samp_com))+
  theme(legend.title = element_blank(),
        aspect.ratio = 1,
        legend.position = 'none')+
  ylim(-1,1)+
  ylab("Relative bias of biomass")+
  xlab("")+
  scale_fill_manual(breaks = c("Reallocation: No -  Likelihood: Yi",
                                "Reallocation: Yes -  Likelihood: Yr",
                                "Reallocation: Yes -  Likelihood: Dj"),
                     values=c("gold","#F8766D","#00BA38"))

@@

q1_plot <- ggplot()+
  geom_boxplot(data = Results_3,
               aes(x = relloc_aggreg,
                   y = q1_com_est,
                   fill = relloc_aggreg),
               outlier.colour = NA)+
  geom_hline(yintercept = 0,linetype="dashed")+
  geom_hline(yintercept = -1,col="red",linetype="dashed")+
  theme_bw()+
  theme(legend.title = element_blank(),
        legend.position = "none",
        aspect.ratio = 1,
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        plot.title = element_text(hjust = 0.5))+
  scale_fill_manual(breaks = c("Reallocation: No -  Likelihood: Yi",
                               "Reallocation: Yes -  Likelihood: Yr",
                               "Reallocation: Yes -  Likelihood: Dj"),
                    values=c("gold","#F8766D","#00BA38"))+
  xlab("")+ylab(parse(text = TeX('$\\xi$')))+
  ggtitle("Zero-inflation parameter")

sigma_plot <- ggplot()+
  geom_boxplot(data = Results_3,
               aes(x = relloc_aggreg,
                   y = sigma_com_est,
                   fill = relloc_aggreg),
               outlier.colour = NA)+
  geom_hline(yintercept = 0,linetype="dashed")+
  theme_bw()+
  theme(legend.title = element_blank(),
        legend.position = "none",
        aspect.ratio = 1,
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        plot.title = element_text(hjust = 0.5))+
  scale_fill_manual(breaks = c("Reallocation: No -  Likelihood: Yi",
                               "Reallocation: Yes -  Likelihood: Yr",
                               "Reallocation: Yes -  Likelihood: Dj"),
                    values=c("gold","#F8766D","#00BA38"))+
  xlab("")+ylab(parse(text = TeX('$\\sigma^2$')))+
  ggtitle("Observation variance parameter")+
  geom_hline(yintercept = 1,col="red",linetype="dashed")

intercept_plot <- ggplot()+
  geom_boxplot(data = Results_3,
               aes(x = relloc_aggreg,
                   y = intercept_est,
                   fill = relloc_aggreg),
               outlier.colour = NA)+
  geom_hline(yintercept = 0,linetype="dashed")+
  theme_bw()+
  theme(legend.title = element_blank(),
        legend.position = "none",
        aspect.ratio = 1,
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        plot.title = element_text(hjust = 0.5))+
  scale_fill_manual(breaks = c("Reallocation: No -  Likelihood: Yi",
                               "Reallocation: Yes -  Likelihood: Yr",
                               "Reallocation: Yes -  Likelihood: Dj"),
                    values=c("gold","#F8766D","#00BA38"))+
  xlab("")+ylab(parse(text = TeX('$\\mu$')))+
  ggtitle("Intercept of the latent field")+
  geom_hline(yintercept = 2,col="red",linetype="dashed")

@@

Results_conv_2 <- summaryBy(converge+one~
                              Model+
                              aggreg_obs,
                            data=Results_conv,
                            FUN=sum) %>%
  dplyr::select(Model,
                aggreg_obs,
                converge.sum,
                one.sum) %>%
    mutate(aggreg_obs = ifelse(aggreg_obs == T,"Dj","Yi"),
           perc_convergence = round((1 - converge.sum / one.sum)*100,digits = 3))

@@

Results_conv_2 <- Results_conv_2[-which(Results_conv_2$Model == "Scientific model" &
                                          Results_conv_2$`Likelihood level` == "Dj"),]
Results_conv_2$`Likelihood level`[which(Results_conv_2$Model == "Scientific model" &
                       Results_conv_2$`Likelihood level` == "Yr")] <- " "

@@

Results_plot$obs <- NA
Results_plot$obs[which(Results_plot$aggreg_obs == T)] <- "Dj"
Results_plot$obs[which(Results_plot$aggreg_obs == F)] <- "Yr"
Results_plot$obs[which(Results_plot$Estimation_model == 2)] <- "Scientific data"
Results_plot$obs <- factor(Results_plot$obs,levels = c("Yr","Dj","Scientific data"))

@@

beta_plot <- ggplot()+
  geom_boxplot(data = Results_plot,
               aes(x = Model,
                   y = beta1_est,
                   fill = obs))+
  geom_hline(yintercept = 0,linetype="dashed")+
  theme_bw()+
  theme(legend.title = element_blank(),
        legend.position = "none",
        aspect.ratio = 1)+
  # facet_wrap(.~simu_type)+
  ylab(TeX("$\\beta_S$")) +
  xlab("")+
  geom_hline(yintercept = 2,col="red",linetype="dashed")+
  scale_color_manual(breaks = c("Scientific model",
                                "Yr",
                                "Dj"),
                     values=c("#619CFF","#F8766D","#00BA38"))

MSPE_S_plot <- ggplot()+
  geom_boxplot(data = Results_plot,
               aes(x = Model,
                   y = mspe,
                   fill = obs))+
  theme_bw()+
  theme(legend.title = element_blank(),
        legend.position = "none",
        aspect.ratio = 1)+
  # facet_wrap(.~simu_type)+
  ylab("MSPE")+xlab("")+
  scale_color_manual(breaks = c("Scientific model",
                                "Yr",
                                "Dj"),
                     values=c("#619CFF","#F8766D","#00BA38"))+
  ylim(0,NA)

Range_plot <- ggplot()+
  geom_boxplot(data = Results_plot,
               aes(x = Model,
                   y = Range,
                   fill = obs))+
  geom_hline(yintercept = 0,linetype="dashed")+
  theme_bw()+
  theme(legend.title = element_blank(),
        legend.position = "none",
        aspect.ratio = 1)+
  # facet_wrap(.~simu_type)+
  ylab("Range")+
  xlab("")+
  geom_hline(yintercept = 0.6,col="red",linetype="dashed")+
  scale_color_manual(breaks = c("Scientific model",
                                "Yr",
                                "Dj"),
                     values=c("#619CFF","#F8766D","#00BA38"))+
  ylim(-0.1,2)

@@

realloc_rest_plot <- ggplot(realloc_rest_df)+
  geom_point(aes(x=x,y=y,col=S_x),shape=15,size=2)+
  scale_color_distiller(palette = "Spectral",limits=c(0,NA))+
  ggtitle("Integrated model",subtitle = "Commercial likelihood on Dj")+
  theme_bw()+
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5))+
  geom_sf(data = mapBase)+
  coord_sf(xlim = c(-6,0), ylim = c(43,48+0.25), expand = FALSE)+
  xlab("")+ylab("")

@@

## Parameter estimates
est_par_df_full_3$lkl[which(est_par_df_full_3$lkl == "Yi")] <- "Yr"
est_par_df_full_3$lkl <- factor(est_par_df_full_3$lkl,levels = c("Dj","Yr","Scientific model"))
est_par_df_full_3 <- est_par_df_full_3 %>%
  filter(par_names != "substr_Sand_Coarse_substrate")
par_plot <- ggplot(est_par_df_full_3, aes(y=par_val, x=par_names))+
  geom_point(
    aes(color = lkl),
    position = position_dodge(0.5),
    size=2
  )+
  geom_errorbar(aes(ymin = CI.inf, ymax = CI.sup, color = lkl),
                position = position_dodge(0.5),width=0.4
  )+
  scale_color_manual(breaks = c("Scientific model",
                                "Yr",
                                "Dj"),
                     values=c("#619CFF","#F8766D","#00BA38"))+
  geom_hline(yintercept=0, linetype="dashed", color = "red",alpha=0.4)+
  xlab("")+ylab("")+
  theme_bw()+
  theme(legend.title = element_blank(),
        legend.position = "none",
        aspect.ratio = 1)+
  coord_flip()+
  scale_x_discrete(labels=c('k_com'=parse(text = TeX('$k_{com}$')),
                            'Sigma_com'=parse(text = TeX('$\\sigma_{com}$')),
                            'q1_com'=parse(text = TeX('$\\xi_{com}$')),
                            'Sigma_sci'=parse(text = TeX('$\\sigma_{sci}$')),
                            'q1_sci'=parse(text = TeX('$\\xi_{sci}$')),
                            'Range'="Range",
                            'MargSD'="Marginale variance",
                            'substr_Mud_sediment'=parse(text = TeX('$\\beta_{S}$')),
                            'intercept'=parse(text = TeX('$\\mu$'))))

>>>>

numbersections : true
floatsintext     : yes
figurelist       : no
tablelist        : no
footnotelist     : no
linenumbers      : yes
mask             : no
draft            : no

@@

## Table of convergence
Results_conv <- Results
Results_conv$one <- 1
Results_conv_2 <- summaryBy(Convergence+one~
                              sequencesdepeche+
                              # zonespersequence+
                              aggreg_obs+
                              # b_true+
                              n_samp_com+
                              reallocation,
                            data=Results_conv,
                            FUN=sum) %>%
  dplyr::select(n_samp_com,
                sequencesdepeche,
                # zonespersequence,
                reallocation,
                aggreg_obs,
                Convergence.sum,
                one.sum) %>%
    mutate(aggreg_obs = ifelse(aggreg_obs == T,"Dk","Yi"),
           reallocation = ifelse(reallocation == 1,"Yes","No"),
           perc_convergence = round((1 - Convergence.sum / one.sum)*100,digits = 3)) %>%
  mutate(aggreg_obs = ifelse((aggreg_obs == "Yi" & reallocation == "Yes"),"Yr",aggreg_obs))

@@

Results <- Results %>%
  mutate(relloc_aggreg = paste0("Reallocation: ",ifelse(reallocation==0,"No","Yes")," -  Likelihood: ",ifelse(aggreg_obs==T,"Dk","Yi"))) %>%
  mutate(relloc_aggreg = ifelse(aggreg_obs == F & reallocation == 1,"Reallocation: Yes -  Likelihood: Yr",relloc_aggreg))

Results$zonespersequence <- as.factor(Results$zonespersequence)
Results$b_true <- as.factor(Results$b_true)
Results$relloc_aggreg <- factor(Results$relloc_aggreg,
                                levels = c("Reallocation: No -  Likelihood: Yi",
                                           "Reallocation: Yes -  Likelihood: Yr",
                                           "Reallocation: Yes -  Likelihood: Dk"))

@@

MSPE_S_plot <- ggplot()+
  geom_boxplot(data = Results_2,
               aes(x = zonespersequence,
                   y = mspe,
                   fill = relloc_aggreg),
               outlier.colour = NA)+
  theme_bw()+
  facet_wrap(.~factor(n_samp_com))+
  theme(legend.title = element_blank(),
        legend.position = "none",
        aspect.ratio = 1)+
  ylab("MSPE")+
  xlab("")+
  scale_y_log10(breaks = trans_breaks("log10", function(x) 10^x),
                labels = trans_format("log10", math_format(10^.x)))+
  scale_fill_manual(breaks = c("Reallocation: No -  Likelihood: Yi",
                                "Reallocation: Yes -  Likelihood: Yr",
                                "Reallocation: Yes -  Likelihood: Dk"),
                     values=c("gold","#F8766D","#00BA38"))

Beta_plot <- ggplot()+
  geom_boxplot(data = Results_2,
               aes(x = zonespersequence,
                   y = beta1_est,
                   fill = relloc_aggreg),
               outlier.colour = NA)+
  geom_hline(yintercept = 0,linetype="dashed")+
  geom_hline(yintercept = 2,col="red",linetype="dashed")+
  theme_bw()+
  facet_wrap(.~factor(n_samp_com))+
  theme(legend.title = element_blank(),
        legend.position = "none",
        aspect.ratio = 1)+
  # ylim(-1,1)+ 
  ylab(parse(text = TeX('$\\beta_S$')))+
  xlab("")+
  scale_fill_manual(breaks = c("Reallocation: No -  Likelihood: Yi",
                                "Reallocation: Yes -  Likelihood: Yr",
                                "Reallocation: Yes -  Likelihood: Dk"),
                     values=c("gold","#F8766D","#00BA38"))

RelBias_N_plot <- ggplot()+
  geom_boxplot(data = Results_2,
               aes(x = zonespersequence,
                   y = RelBias_N,
                   fill = relloc_aggreg),
               outlier.colour = NA)+
  geom_hline(yintercept = 0,linetype="dashed")+
  theme_bw()+
  facet_wrap(.~factor(n_samp_com))+
  theme(legend.title = element_blank(),
        aspect.ratio = 1,
        legend.position = 'none')+
  ylim(-1,1)+
  ylab("Relative bias of biomass")+
  xlab("")+
  scale_fill_manual(breaks = c("Reallocation: No -  Likelihood: Yi",
                                "Reallocation: Yes -  Likelihood: Yr",
                                "Reallocation: Yes -  Likelihood: Dk"),
                     values=c("gold","#F8766D","#00BA38"))

@@

q1_plot <- ggplot()+
  geom_boxplot(data = Results_3,
               aes(x = relloc_aggreg,
                   y = q1_com_est,
                   fill = relloc_aggreg),
               outlier.colour = NA)+
  geom_hline(yintercept = 0,linetype="dashed")+
  geom_hline(yintercept = -1,col="red",linetype="dashed")+
  theme_bw()+
  theme(legend.title = element_blank(),
        legend.position = "none",
        aspect.ratio = 1,
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        plot.title = element_text(hjust = 0.5))+
  scale_fill_manual(breaks = c("Reallocation: No -  Likelihood: Yi",
                               "Reallocation: Yes -  Likelihood: Yr",
                               "Reallocation: Yes -  Likelihood: Dk"),
                    values=c("gold","#F8766D","#00BA38"))+
  xlab("")+ylab(parse(text = TeX('$\\xi$')))+
  ggtitle("Zero-inflation parameter")

sigma_plot <- ggplot()+
  geom_boxplot(data = Results_3,
               aes(x = relloc_aggreg,
                   y = sigma_com_est,
                   fill = relloc_aggreg),
               outlier.colour = NA)+
  geom_hline(yintercept = 0,linetype="dashed")+
  theme_bw()+
  theme(legend.title = element_blank(),
        legend.position = "none",
        aspect.ratio = 1,
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        plot.title = element_text(hjust = 0.5))+
  scale_fill_manual(breaks = c("Reallocation: No -  Likelihood: Yi",
                               "Reallocation: Yes -  Likelihood: Yr",
                               "Reallocation: Yes -  Likelihood: Dk"),
                    values=c("gold","#F8766D","#00BA38"))+
  xlab("")+ylab(parse(text = TeX('$\\sigma^2$')))+
  ggtitle("Observation variance parameter")+
  geom_hline(yintercept = 1,col="red",linetype="dashed")

intercept_plot <- ggplot()+
  geom_boxplot(data = Results_3,
               aes(x = relloc_aggreg,
                   y = intercept_est,
                   fill = relloc_aggreg),
               outlier.colour = NA)+
  geom_hline(yintercept = 0,linetype="dashed")+
  theme_bw()+
  theme(legend.title = element_blank(),
        legend.position = "none",
        aspect.ratio = 1,
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        plot.title = element_text(hjust = 0.5))+
  scale_fill_manual(breaks = c("Reallocation: No -  Likelihood: Yi",
                               "Reallocation: Yes -  Likelihood: Yr",
                               "Reallocation: Yes -  Likelihood: Dk"),
                    values=c("gold","#F8766D","#00BA38"))+
  xlab("")+ylab(parse(text = TeX('$\\mu$')))+
  ggtitle("Intercept of the latent field")+
  geom_hline(yintercept = 2,col="red",linetype="dashed")

@@

Results_conv_2 <- summaryBy(converge+one~
                              Model+
                              aggreg_obs,
                            data=Results_conv,
                            FUN=sum) %>%
  dplyr::select(Model,
                aggreg_obs,
                converge.sum,
                one.sum) %>%
    mutate(aggreg_obs = ifelse(aggreg_obs == T,"Dk","Yi"),
           perc_convergence = round((1 - converge.sum / one.sum)*100,digits = 3))

@@

Results_conv_2 <- Results_conv_2[-which(Results_conv_2$Model == "Scientific model" &
                                          Results_conv_2$`Likelihood level` == "Dk"),]
Results_conv_2$`Likelihood level`[which(Results_conv_2$Model == "Scientific model" &
                       Results_conv_2$`Likelihood level` == "Yr")] <- " "

@@

Results_plot$obs <- NA
Results_plot$obs[which(Results_plot$aggreg_obs == T)] <- "Dk"
Results_plot$obs[which(Results_plot$aggreg_obs == F)] <- "Yr"
Results_plot$obs[which(Results_plot$Estimation_model == 2)] <- "Scientific data"
Results_plot$obs <- factor(Results_plot$obs,levels = c("Yr","Dk","Scientific data"))

@@

beta_plot <- ggplot()+
  geom_boxplot(data = Results_plot,
               aes(x = Model,
                   y = beta1_est,
                   fill = obs))+
  geom_hline(yintercept = 0,linetype="dashed")+
  theme_bw()+
  theme(legend.title = element_blank(),
        legend.position = "none",
        aspect.ratio = 1)+
  # facet_wrap(.~simu_type)+
  ylab(TeX("$\\beta_S$")) +
  xlab("")+
  geom_hline(yintercept = 2,col="red",linetype="dashed")+
  scale_color_manual(breaks = c("Scientific model",
                                "Yr",
                                "Dk"),
                     values=c("#619CFF","#F8766D","#00BA38"))

MSPE_S_plot <- ggplot()+
  geom_boxplot(data = Results_plot,
               aes(x = Model,
                   y = mspe,
                   fill = obs))+
  theme_bw()+
  theme(legend.title = element_blank(),
        legend.position = "none",
        aspect.ratio = 1)+
  # facet_wrap(.~simu_type)+
  ylab("MSPE")+xlab("")+
  scale_color_manual(breaks = c("Scientific model",
                                "Yr",
                                "Dk"),
                     values=c("#619CFF","#F8766D","#00BA38"))+
  ylim(0,NA)

Range_plot <- ggplot()+
  geom_boxplot(data = Results_plot,
               aes(x = Model,
                   y = Range,
                   fill = obs))+
  geom_hline(yintercept = 0,linetype="dashed")+
  theme_bw()+
  theme(legend.title = element_blank(),
        legend.position = "none",
        aspect.ratio = 1)+
  # facet_wrap(.~simu_type)+
  ylab("Range")+
  xlab("")+
  geom_hline(yintercept = 0.6,col="red",linetype="dashed")+
  scale_color_manual(breaks = c("Scientific model",
                                "Yr",
                                "Dk"),
                     values=c("#619CFF","#F8766D","#00BA38"))+
  ylim(-0.1,2)

@@

realloc_rest_plot <- ggplot(realloc_rest_df)+
  geom_point(aes(x=x,y=y,col=S_x),shape=15,size=2)+
  scale_color_distiller(palette = "Spectral",limits=c(0,NA))+
  ggtitle("Integrated model",subtitle = "Commercial likelihood on Dk")+
  theme_bw()+
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5))+
  geom_sf(data = mapBase)+
  coord_sf(xlim = c(-6,0), ylim = c(43,48+0.25), expand = FALSE)+
  xlab("")+ylab("")

@@

## Parameter estimates
est_par_df_full_3$lkl[which(est_par_df_full_3$lkl == "Dj")] <- "Dk"

est_par_df_full_3$lkl[which(est_par_df_full_3$lkl == "Yi")] <- "Yr"
est_par_df_full_3$lkl <- factor(est_par_df_full_3$lkl,levels = c("Dk","Yr","Scientific model"))
est_par_df_full_3 <- est_par_df_full_3 %>%
  filter(par_names != "substr_Sand_Coarse_substrate")
par_plot <- ggplot(est_par_df_full_3, aes(y=par_val, x=par_names))+
  geom_point(
    aes(color = lkl),
    position = position_dodge(0.5),
    size=2
  )+
  geom_errorbar(aes(ymin = CI.inf, ymax = CI.sup, color = lkl),
                position = position_dodge(0.5),width=0.4
  )+
  scale_color_manual(breaks = c("Scientific model",
                                "Yr",
                                "Dk"),
                     values=c("#619CFF","#F8766D","#00BA38"))+
  geom_hline(yintercept=0, linetype="dashed", color = "red",alpha=0.4)+
  xlab("")+ylab("")+
  theme_bw()+
  theme(legend.title = element_blank(),
        legend.position = "none",
        aspect.ratio = 1)+
  coord_flip()+
  scale_x_discrete(labels=c('k_com'=parse(text = TeX('$k_{com}$')),
                            'Sigma_com'=parse(text = TeX('$\\sigma_{com}$')),
                            'q1_com'=parse(text = TeX('$\\xi_{com}$')),
                            'Sigma_sci'=parse(text = TeX('$\\sigma_{sci}$')),
                            'q1_sci'=parse(text = TeX('$\\xi_{sci}$')),
                            'Range'="Range",
                            'MargSD'="Marginale variance",
                            'substr_Mud_sediment'=parse(text = TeX('$\\beta_{S}$')),
                            'intercept'=parse(text = TeX('$\\mu$'))))

### 2022-10-21 Version_M2_plusieurszones/pres/AFH_2022/AFH_2022.Rmd
modif

---
title: "Downscaling coarse observations to predict continuous species spatio-temporal distribution"
subtitle : "Going from coarse landings data to fine scale fish distribution"
author : "Baptiste Alglave, Marie-Pierre Etienne, Kasper Kristensen, Youen Vermard, Mathieu Woillez, Etienne Rivot"

>>>>

---
title: "Inferring fine scale wild species distribution from spatially aggregated data"
author : "Marie-Pierre Etienne, Baptiste Alglave, Kasper Kristensen, Youen Vermard, Mathieu Woillez, Etienne Rivot"
